Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2017-04-26 teaching.tex
finish second, simiple version of teaching model

>>>>

\vskip.5in
\section{3-player version, Reunification better than Status Quo}
Let us now consider a case where the payoffs for the secessionists are \underline{lower} in the unrecognized state ('Status Quo') than they are if they cede and rejoin the home state. We believe this will be the case a few months or years after they take control of the territory and unrecognized status has caused their economic situation to deteriorate.

\subsection{Players and Strategy Spaces}
Same as in Section 1.

\vskip.3in
\subsection{Timing and Information}
Same as in Section 1.

\vskip.5in
\subsection{Payoffs}
\begin{itemize}
	\item The payoffs after ($SQ,SQ$) are $-p,3,\bm{0}+p$
	\item The payoffs after ($SQ,C$) are $-10-p,5,1$
	\item The payoffs after ($C,SQ$) are $3-p,0,5+p$
	\item The payoffs after ($C,C$) are $-p,3,\bm{0}$
\end{itemize}
The only change(s) from Section 1 is that the secessionist's payoff from ($SQ,SQ$) has been reduced, and the payoffs from ($C,C$) along with it.

\vskip.5in
\subsection{Analysis}
We proceed by backward induction.
\begin{itemize}
	\item In the simultaneous game between $G$ and $S$, $C$ is dominated by $SQ$ for player $G$.
		\begin{itemize}
			\item Therefore the Nash Equilibrium (NE) of the subgame is determined by $p$: 
				\begin{itemize}
					\item If $0+p \geq 1$ (i.e. $p \geq 1$), the NE is ($SQ,SQ$).
					\item If $0+p \leq 1$ (i.e. $p \leq 1$), the NE is ($SQ,C$).
				\end{itemize}
		\end{itemize}
	\item The Patron's decision: if ($SQ,SQ$) is the equilibrium in the subgame, the Patron will get a payoff of $-p$. If ($SQ,C$) is the equilibrium in the subgame, the Patron will get a payoff of $-10-p$.
		\begin{itemize}
			\item Since ($SQ,C$) is the worse outcome for the Patron, the patron does not want to invest at all ($p=0$) if ($SQ,C$) is going to be the outcome. 
				\begin{itemize}
					\item In this case, the Patron chooses $p=0$ and the Patron's total payoff is $-10$.
				\end{itemize}
			\item The Patron prefers ($SQ,SQ$), but to make this happen the Patron must make an investment of the $p \geq 1$. Because the Patron's payoff is $-p$, the Patron maximizes its payoffs in this case where it induces ($SQ,SQ$) by choosing the smallest $p$, which is $p=1$. 
				\begin{itemize}
					\item In this case, the Patron chooses $p=1$ and the Patron's total payoff is $-1$.
				\end{itemize}
			\item Since $-1 > -10$, the Patron will choose to invest $p=1$.
		\end{itemize}
\end{itemize}
Therefore the Subgame Perfect Nash Equilibrium is $p=1$, and ($SQ,SQ$) as long as $p \geq 1$, ($SQ,C$) if $p \leq 1$.
\begin{itemize}
	\item $p=1$, ($SQ,SQ$) is an equilibrium outcome.
	\item $p=1$, ($SQ,C$) is also an equilibrium outcome. You can rule this one out by specifying that the Secessionists choose $SQ$ whenever they are indifferent.
\end{itemize}
